ZPY: Open Source Synthetic Data for Computer Vision

### 2021-07-09 docs/paper/paper.tex
intro, references

\begin{abstract}
Synthetic data presents a unique solution to the huge data requirements of computer vision with deep learning. In this work, we present zpy \footnote{All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}}, an open source framework for creating synthetic data. Built on top of the popular open source 3D platform Blender. And designed with modularity and readability in mind.
\end{abstract}

@@

Open source machine learning frameworks (references)

Deep learning has exploded in popularity due to large open source frameworks such as tensorflow and pytorch

What is synthetic data.

Usecases for synthetic data

autonomous vehicles \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}

pose estimation for humans \ref{shermeyer2020rareplanes}, \ref{shermeyer2020rareplanes}

person re-id \ref{shermeyer2020rareplanes}

detection in overhead satellite imagery \ref{shermeyer2020rareplanes}

pose estimation of satellites in space \ref{kisantal2020satellite}

segmentation of clouds \ref{shermeyer2020rareplanes}

Challenges with synthetic data

We dive deeper into the effects of training curriculum on synthetic data in \ref{sec:curicculum}.

Sim2Real Gap and domain randomization. We perform an ablation study on different types of domain randomization in \ref{sec:domainrandomization}

Black box nature of ML

Other attempts at open source synthetic data \cite{denninger2019blenderproc} \cite{bpycv}

For a thorough review of synthetic data literature, we recommend readers go through Nikolenkos 2019 summary paper \cite{nikolenko2019synthetic}.

>>>>

\begin{abstract}
Synthetic data presents a unique solution to the huge data requirements of computer vision with deep learning. In this work, we present zpy \footnote{All code is available on GitHub at \url{http://github.com/ZumoLabs/zpy}}, an open source framework for creating synthetic data. Built on top of the popular open source 3D platform Blender, zpy is designed with accessibility and readability in mind. Open source synthetic data toolkits like zpy are the bridge between the more mature tools of the 3D workflow and the machine learning frameworks. We make the case for why open source synthetic data is important to solve issues such as fairness and bias by democratizing access to data.
\end{abstract}

@@

Synthetic data is data that is \emph{created} as opposed to \emph{collected}.

Simulation heavy fields were amongst the first to start using synthetic images to start training deep learning systems. Research with the biggest datasets and highest quality can be found in this field, with works on autonomous vehicles \cite{prakash2020structured} \cite{srivastava2019multi} \cite{Hahner_2019} \cite{7780721}, robotic grasping \cite{james2019simtoreal} \cite{tobin2017domain}, and even drone racing \cite{Loquercio_2020}. The availability of high quality 3D humans from the video game and movie industries has also made possible applications such as human pose estimation  \cite{shrivastava2017learning} \cite{Varol_2017}, and person re-id \cite{aaronASRC}. We dive into what synthetic data could mean for human issues such as fairness and bias in \ref{sec:motivation}. Synthetic data has also been used to advance climate and space science, finding applications in detection in overhead satellite imagery \cite{shermeyer2020rareplanes}, pose estimation of satellites in space \cite{kisantal2020satellite}, and segmentation of clouds \cite{lyu2020learning}. Other work has dived deeper into the fundamental theory of synthetic data \cite{le2017using}. For a thorough review of synthetic data literature, we recommend readers go through Nikolenkos 2019 summary paper \cite{nikolenko2019synthetic}.

Analogous to the early days of deep learning, synthetic data still has a black box nature. How to properly create and use synthetic data is not fully understood, and overcoming challenges such as the sim2real gap are still alchemy. We perform an ablation study to examine the effects of domain randomization on synthetic data in \ref{sec:domainrandomization}, and explore the importance of training curriculum in \ref{sec:curicculum}.

Part of the maturation process of deep learning has been the emergence of large open source frameworks such as TensorFlow \cite{tensorflow} and PyTorch \cite{pytorch}. These tools have hundreds of thousands of developers worldwide, and will be the backbone of the AI technologies of the future. As synthetic data itself matures, there too we will see similar open source frameworks emerge. A critical piece of the synthetic data stack, the 3D worfklow, has already produced a champion: Blender \cite{blender}. We study the unique properties of Blender and why it emerged as the frontrunner in the 3D workflow race in \ref{sec:3d}. In fact, zpy is already one of several early attempts at an open source synthetic data toolkit \cite{denninger2019blenderproc} \cite{bpycv}.
